Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-19 Draft.Rmd
Update Draft.Rmd

origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
```
## Wrangling
```{r Predictors}
## Use 80% of data for training
train <- origin %>% 
    slice(1:40)

## Use 20% for testing
test <- origin %>% 
    slice(41:50)

>>>>

origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
```
## Wrangling
```{r Predictors}
## Split origin dataset into 80/20
dat_split <- initial_split(origin, prop =.8)
dat_split

## Use 80% of data for training 
train <- training(dat_split)
